A comparison of design-based and model-based approaches for spatial data.

### 2021-09-14 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
Updated simulations to include 48 settings and be run in a single .r file.

>>>>

<!-- Notes from today -->
<!-- •	Finite populations require a smaller scope but we need to discuss the impact of infinite populations as well – put finite vs infinite population context in the introduction / similarities and differences -->
<!-- •	What should a lower sample size be? 50 seems reasonable 30 may be too small – maybe 50, 100, 200 -->
<!-- •	IRS results seem off for dependent error sample size 50 -->
<!-- •	Take home points – don’t have to do GRTS design with GRTS sample -->
<!-- •	Take home points – GRTS is better for both model and design, while spatial approach for design is close to spatial model -->
<!-- •	Add medium dependence -->
<!-- •	Remind readers what choices of the four approaches in the application mean – what do they mean to practitioners -->
